### 2011-12-04 paper_draft.tex
Moved the paper draft into its own file, plos_template.tex should only contain the template

\section*{Introduction}
Genome Wide Association Studies (GWAS) are an easy and cheap way to find Single Nucleotide Polymorphisms (SNPs) which can be interesting because of their medical relevance. SNPs found through GWAS can be used to find candidate genes for a closer inspection or to predict disease risks. Genome Wide Association Studies make use of statistics to compare the alleles of patients to the alleles of healthy controls. By this the method does not allow to find causal differences but mere correlations. The first GWAS was published in 2005 and compared age-related macular degeneration in contrast to a healthy control group (doi:10.1126/science.1109557). Since the beginning the number of participants in those studies is rising and over 1200 GWAS have been performed (doi:10.1186/1471-2350-10-6.) and over 5000 SNPs have been linked to different diseases and traits in those studies %(http://www.genome.gov/page.cfm?pageid=26525384&clearquery=1#result_table).

>>>>

\section*{Introduction}

Paragraph1:

Investigate the link between genetic variation and phenotypic change
Important because of desease stuff.

Tool used: Genome Wide Association Studies.
--> Describe in one sentence.
--> 2005 first study
--> Today 1200 GWAS performed

genetic markers usually SNPs.
SNPs definition. Allele definition.
SNP can be linked to a phenotypic trait (around 5000 linked to desease)

Paragraph2:

How to obtain data for GWAS?
--> SNPChip, used in many different species
--> Now different companies for DTC genetic testing.
--> Test results provided to customer and raw data
--> Raw data can be used for GWAS, but closed

Paragraph3:

RAW data from 1000 of individuals could be used for multiple scientific
purposes
---> Large potential dataset Are the numbers available for dataset size used
in scientic studies? 2005 93, 2008 500, 2011 23andme 100000? Plot?

Resolution of the problem: Open Science
Create repository for sharing this information. openSNP

Paragraph4:

Describe openSNP:
Open Source, non-commercial
Open Data
Community driven --> Crowd sourcing

Parses data from 23andMe deCODEme....
--> Publications crawler (Maybe mention mendeley price?)
        --PLOS and Mendeley

Advantages for scientists: See paragraph 3

Advantages for customers: 
-->Make sense of the data
-->Contribute to the public domain

Genome Wide Association Studies (GWAS) are an easy and cheap way to find Single Nucleotide Polymorphisms (SNPs) which can be interesting because of their medical relevance. SNPs found through GWAS can be used to find candidate genes for a closer inspection or to predict disease risks. Genome Wide Association Studies make use of statistics to compare the alleles of patients to the alleles of healthy controls. By this the method does not allow to find causal differences but mere correlations. The first GWAS was published in 2005 and compared age-related macular degeneration in contrast to a healthy control group (doi:10.1126/science.1109557). Since the beginning the number of participants in those studies is rising and over 1200 GWAS have been performed (doi:10.1186/1471-2350-10-6.) and over 5000 SNPs have been linked to different diseases and traits in those studies %(http://www.genome.gov/page.cfm?pageid=26525384&clearquery=1#result_table).
